Survey of Cache Oblivious B-trees

### 2011-12-12 paper.tex
fix the modifications lost during merge

In order for B-trees to remain versatile, they must be able to accommodate
various forms of data. However, traditional B-trees and string B-trees have
suboptimal performance when variable length strings are used as keys. In
addition, string B-trees do not support compression, and commonly used front
compression is handled sub-optimally. Regular B-trees and string B-trees are
not cache oblivious, and thus incur poorer performance as described previously.
In \cite{BenderFaKu06}, Bender et al. address these issues by designing a Cache
Oblivious String B-tree (COSB-tree), which they argue works efficiently for
variable length string keys. They also provide a modified front-compression
scheme, which gives their approach the advantages of using less space and
having improved locality within the compressed data.

>>>>

In order for B-trees to remain versatile, they must be able to accommodate
various forms of data. Bender et al. argue the following weaknesses in
existing B-tree designs: 
\begin{inparaenum}[(a)]
  \item traditional B-trees have suboptimal performance when variable length
  strings are used as keys \cite{BenderDemainColton},
  \item string B-trees \cite{Ferragina98} handle variable-length strings well
  but do not use compression, 
  \item front compression \cite{BayerUn77,ClarkSaSt69,Comer79,Wagner73} is used
  in many B-trees, but is handled sub-optimally \cite{BenderFaKu06}. 
\end{inparaenum}

In \cite{BenderFaKu06}, Bender et al. address these issues by designing a Cache
Oblivious String B-tree (COSB-tree), which they argue works more efficiently
for variable length string keys. They also provide a modified front-compression
scheme, which lets their data structure use less space and have improved
compressed data locality.
